Parsing Postfix log files

### 2008-08-06 doc/logparser-background.tex
Part two of the great renaming complete. Graphs still need to be renamed.

If the database supports sub-selects percentages can be obtained for the
top ten restrictions:

@@

\begin{table}[ht]
    \caption{Truncated sample output from SQL query showing percentages}
    \empty{}\label{Truncated sample output from SQL query showing
    percentages}
    \begin{tabular}[]{lrr}
        \tableline{}
        Restriction & Number of hits & Percentage of hits \\
        \tableline{}%
        \input{build/sample-sql-output-include.tex}
        \tableline{}
    \end{tabular}
\end{table}

@@

        \begin{table}[ht]
            \caption{Summary of rejections}\label{Summary of rejections}
            \input{build/restriction-table-include.tex}
        \end{table}

>>>>

If the database supports sub-selects percentages can be obtained for the
top ten restrictions (sample output shown in \tableref{Truncated sample
output from SQL query showing percentages}):

XXX GENERATE THE FOLLOWING FROM THE SQL FILE FED TO SQLITE\@.

@@

\begin{table}[ht]
    \caption{Truncated sample output from SQL query showing percentages}
    \empty{}\label{Truncated sample output from SQL query showing
    percentages}
    \begin{tabular}[]{lrr}
        \tableline{}
        Restriction & Number of hits & Percentage of hits \\
        \tableline{}%
        \input{build/include-sample-sql-output}
        \tableline{}
    \end{tabular}
\end{table}

@@

        \begin{table}[ht]
            \caption{Summary of rejections}\label{Summary of rejections}
            \input{build/include-restriction-summary-table}
        \end{table}

### 2008-08-06 doc/logparser-results.tex
Part two of the great renaming complete. Graphs still need to be renamed.

\showtable{build/mails-received-include-for-graph}{Number of mails received
via SMTP per day}{Number of mails received per day: statistics}

@@

Parsing all \numberOFlogFILES{} log files in one run took
\input{build/timing-run-include.tex}.  The computer was dedicated to the
task of gathering statistics from test runs, and was not used for any other
purpose while test runs were ongoing; any services not necessary for
running the tests were disabled.

@@

\showtable{build/stats-normal-filesize-line-count-include}{Ratio of file
size and number of lines to parsing time}{parsing time vs file size vs
number lines factor table}

@@

\showtable{build/stats-normal-shuffle-reverse-include}{Parsing time
relative to shuffled ordering}{Parsing time relative to shuffled ordering
table}

@@

It is clear from \graphref{Percentage parsing time increase of maximum
ruleset over minimum ruleset} that the increased number of rules noticeably
increases parsing time with reverse ordering, and to a lesser extent with
shuffled ordering.  The normal ordering (where are the most frequently
matching rules are tried first) shows a mean increase of
\input{build/full-ruleset-vs-minimum-ruleset-include.tex} in parsing time
for a \numberOFrulesMAXIMUMpercentage{} increase in the number of rules.
Log files 22 and 62--68 show much smaller increases for shuffled and
reversed ordering than other log files do, because the majority of log
lines in those log files are parsed by Postfix components with a small
number of parsing rules, so removing unnecessary rules has little effect on
the total number of rules used.  These results show that the architecture
scales very well as the number of rules increases, and that optimally
sorting the rules is an important optimisation contributing to this
scalability.

@@

\showtable{build/stats-cached-discarded-include-for-graph} {Increase in
parsing time when not caching compiled regexes} {Increase in parsing time
when not caching compiled regexes table}

>>>>

\showtable{build/include-mails-received-table}{Number of mails received via
SMTP per day}{Number of mails received per day: statistics}

@@

Parsing all \numberOFlogFILES{} log files in one run took
\input{build/include-timing-run-duration}.  The computer was dedicated to
the task of gathering statistics from test runs, and was not used for any
other purpose while test runs were ongoing; any services not necessary for
running the tests were disabled.

@@

\showtable{build/include-file-size-and-number-of-lines-vs-parsing-time}{Ratio
of file size and number of lines to parsing time}{parsing time vs file size
vs number lines factor table}

@@

\showtable{build/include-normal-and-reverse-vs-shuffle}{Parsing time
relative to shuffled ordering}{Parsing time relative to shuffled ordering
table}

@@

It is clear from \graphref{Percentage parsing time increase of maximum
ruleset over minimum ruleset} that the increased number of rules noticeably
increases parsing time with reverse ordering, and to a lesser extent with
shuffled ordering.  The normal ordering (where are the most frequently
matching rules are tried first) shows a mean increase of
\input{build/include-full-ruleset-vs-minimum-ruleset} in parsing time for a
\numberOFrulesMAXIMUMpercentage{} increase in the number of rules.  Log
files 22 and 62--68 show much smaller increases for shuffled and reversed
ordering than other log files do, because the majority of log lines in
those log files are parsed by Postfix components with a small number of
parsing rules, so removing unnecessary rules has little effect on the total
number of rules used.  These results show that the architecture scales very
well as the number of rules increases, and that optimally sorting the rules
is an important optimisation contributing to this scalability.

@@

\showtable{build/include-cached-regexes-vs-discarded-regexes} {Increase in
parsing time when not caching compiled regexes} {Increase in parsing time
when not caching compiled regexes table}
